Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-01 paper/paper.qmd
Update paper.qmd

The main focus of our analysis is the percentage of support for Harris,
which we will model using various predictor variables. We are
particularly interested in how the end date, polling organization,
state, and poll score affect voter support. Using a linear regression
framework, we can quantify the relationships between these predictors
and the support outcome, providing clarity on how each factor influences
overall support for Harris. As Silver (2012) argues, leveraging aggregated
data from multiple reputable sources and adjusting for sample quality
and methodology is crucial for achieving accurate predictions.
By estimating the coefficients for each predictor, we aim to draw
significant conclusions about their respective impacts on voter
sentiment.

>>>>

The main focus of our analysis is the percentage of support for Harris,
which we will model using various predictor variables. We are
particularly interested in how the end date, polling organization,
state, and poll score affect voter support. Using a linear regression
framework, we can quantify the relationships between these predictors
and the support outcome, providing clarity on how each factor influences
overall support for Harris. By estimating the coefficients for each 
predictor, we aim to drawn significant conclusions about their respective
impacts on voter sentiment.
